---
name: Adrian
surname: Stanciu
position: "Post Doctoral Researcher"
address: "GESIS-Leibniz Institute for the Social Sciences"
www: adrianstanciu.eu
email: "Adrian.Stanciu@gesis.org"
twitter: adrianvstanciu
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Research interests

Ageing, assessment theory, cross-cultural research, individual and cultural change, 
inter-individual and inter-group relations, stereotypes, values. 

# Current & Past Positions

```{r}
library(tibble)
tribble(
  ~ Job, ~ Year, ~ Institution, ~ Location,
  "Post-Doc", "2021-", "GESIS-Leibniz Institute for the Social Sciences", "Mannheim, DE",
  "Visiting Scholar", "2017- ", "Jacobs University Bremen", "Bremen, De",
  "Post-Doc", "2017-20", "Vechta University", "Vechta, DE",
  "Visiting Researcher", "2018.11", "Sparc Group, ICS", "Lisbon, PT",
  "Research Associate", "2016-17", "Jacobs University Bremen", "Bremen, DE",
  "Teaching Assistant", "2016.02-03", "Jacobs Unviersity Bremen", "Bremen, DE",
  "Research Assistant", "2015-16", "Jacobs Unviersity Bremen", "Bremen, DE",
  "Research Associate", "2012.04-05", "University of Groningen", "Groningen, NL",
  "Teaching Assistant", "2011-12", "University of Groningen", "Groningen, NL",
  "Teaching Assistant", "2011.01-07", "University of Groningen", "Groningen, NL",
  "Research Assistant", "2009-11", "University of Groningen", "Groningen, NL",
  "Student Assistant", "2008-09", "University of Bucharest", "Bucharest,RO"
) %>% 
  detailed_entries(Job, Year, Institution, Location)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Location,
  "PhD Psychology", "2012-17", "BIGSSS", "Bremen, DE",
  "Msc Behavioral and Social Sciences", "2009-11", "University of Groningen", "Groningen, NL",
  "BA Sociology", "2006-09", "University of Bucharest", "Bucharest, RO"
) %>% 
  detailed_entries(Degree, Year, Institution, Location)
```

# Further training

```{r}
tribble(
  ~ Topic, ~ Year, ~ Institution, ~ Location,
  "Methods: Introduction to Data Science with Python", "2019.07", "GESIS-Leibniz Institute for the Social Sciences", "Cologne, DE",
  "Summer School: Cultural Genomics", "2014.07", "IACCP Congress", "Reims, FR",
  "Methods: Desining and Implementation of Longitudinal Surveys", "2013.08", "GESIS-Leibniz Institute for the Social Sciences", "Cologne, DE",
  "Methods: Communication and Cultural Dynamics", "2013.02", "University of Groningen", "Groningen, NL",
  "Summer School: Applied Multivariate Statistics", "2009.08", "Utrecht University", "Utrecht, NL"
) %>% 
  detailed_entries(Topic, Year, Institution, Location)
```

# Awards & Grants

```{r}
tribble(
  ~ What, ~ Year, ~ Institution,
  "[short listed] Open Call for Independent Projects for Post-Docs", "2020", "Central Research Developmental Fund, University of Bremen",
  "German Academic Exchange (DAAD) travel grant", "2018,15", "IACCP Congress",
  "Witkon-Okonji travel grant", "2017,16", "IACCP Congress",
  "Stipend for doctoral dissertation completion", "2016", "FAZIT Stiftung",
  "Research stay grant for ISCTE-Lisbon, PT", "2015", "BIGSSS"
) %>% 
  detailed_entries(What, Year, Institution)
```

# Teaching

```{r}
tribble(
  ~ What, ~ Semst, ~ Type, ~ Institution,
  "Vielfalt der Altersbildern und deren Auswirkung", "WiSe2020/21", "Guest-contribution in eGenerale online Course", "University of Bremen, DE",
  "Heterogenitaet des Alterns aus psychologischer Perspektive", "WiSe2018/19;SoSe2019,20", "Seminar", "University of Vechta, DE",
  "Introduction to Reading and Understanding Research Articles in Psychology", "SoSe2018,19;WiSe2019/20", "Seminar", "University of Vechta, DE",
  "Psychologische Forschung zu Altersbildern-Entstehung und Folgen", "WiSe2018/19,19/20", "Seminar", "University of Vechta, DE",
  "Current Debates in Group Processes and Intergroup Relations", "WiSe2017/18", "Seminar", "Jacobs University Bremen, DE",
  "(Mediated) Intercultural Communication (ta)", "SoSe2016", "Course", "Jacobs University Bremen, DE",
  "Introduction to Empirical Research and Research Design (ta)", "WiSe2013/14", "Course", "Jacobs University Bremen, DE",
  "Dynamics of Research: From an Idea to a Manuscript", "2018.08", "Workshop", "Mircea Vulcanescu Summer School, RO", 
  "Statistics 1A&B (ta)", "WiSe2011/12;SoSe2012", "Tutorial", "University of Groningen, NL",
  "Research Practicum (ta)", "SoSe2011", "Tutorial", "University of Groningen, NL"
) %>% 
  detailed_entries(What, Semst, Type, Institution)
```

# Academic Contributions

## Peer-Reviewed

```{r}
library(dplyr)
knitr::write_bib(c("article"), "peerrev.bib")

bibliography_entries("peerrev.bib") %>%
  arrange(desc(author$family))
```

## Pre-Prints

```{r}
knitr::write_bib(c("article"), "preprint.bib")

bibliography_entries("preprint.bib") %>%
  arrange(desc(author$family))
```

## Book Contributions

```{r}
knitr::write_bib(c("incollection","book"), "books.bib")

bibliography_entries("books.bib") %>%
  arrange(desc(author$family))
```

## In Review Manuscripts

## Conference Contributions

## Organizational Tasks

# Language & Methods

```{r}
tribble(
  ~ Skill, ~ What,
  "Languages", "Romanian, English, German",
  "Methods", "Analysis of Variance, Regression, SEM, Data Reduction (EFA, CFA, MDS, Cluster Analysis), Multilevel Analysis, Simulations",
  "Software", "SPSS, AMOS, Mplus, R, MsOffice"
) %>% 
  detailed_entries(What, Skill)
```

# Other Activities

```{r}
tribble(
  ~ What, ~ List, ~ Period,
  "Editorial", "Associate Editor at Online Readings in Psychology and Culture", "2020-"
) %>% 
  detailed_entries(What, List, Period)
```


